Relationship between solar wind, $D_{st}$, and plasmasphere trough mass density on one-hour time scales

### 2016-04-28 paper.tex
Updating table parsing and interpolation code
misc paper.tex edits

Because the dynamics of the magnetopshere take place on a time scale of less than one day, we have also considered hourly averages as shown in the top panel of \ref{HourlyAveragedDstEvents}.  A total of 668 events were found in the interval of May 1983 through August 1991 with an average duration of 9 hours and a median duration of 3 hours.  The error bars were computed in the same way as \ref{DailyAveragedDstEvents}.  In this plot, the overall trend is similar to that found in the bottom panel of \ref{HourlyAveragedDstEvents} - $\rho_{eq}$ is slighly elevated at the time of the threhshold crossing of $D_{st}$ with respect to the values one day before and after, but the elevation is small and in general not statistically significant.  At this timescale no obvious change in mass density at hourly timescale is visible. This points to an issue with only looking at long-timescale trends between density and $D_{st}$, and allows for the possibility that other factors are influencing the long term correlation because there is no obvious connection on a short timescale.  One possibility is that, as suggested in \cite{Takahashi2010}, $F_{10.7}$ plays a significant role in driving long term density values which biases the long-term correlation of density and $D_{st}$.
=======
Results of test on different between means of $\rho_{eq}$ shown in the bottom panel of \ref{DailyAverage} on days near or on the day of a $D_{st}$ event.

@@

\begin{figure}[htp!]
\centering
\includegraphics[scale=0.45]{paperfigures/alldata-GOES6-1983-1991.eps}
\caption{Overview of data used in this study. The top four panels show parameters from \cite{Kondrashov2014ReconstructionOfGaps} and the bottom panel contains $\rho_{eq}$ based on GOES 6 measurements from \cite{Denton} after interpolation and averaging described in the text. Dashed horizontal lines in the $D_{st}$ and $\rho_{eq}$ panels indicate sample event cutoff thresholds of $D_{st} = -50$~nT and $\rho_{eq} = 40$~amu/cm$^3$}.
\label{AllData}
\end{figure}

>>>>

Because the dynamics of the magnetopshere take place on a time scale of less than one day, we have also considered hourly averages as shown in the top panel of \ref{HourlyAveragedDstEvents}.  A total of 668 events were found in the interval of May 1983 through August 1991 with an average duration of 9 hours and a median duration of 3 hours.  The error bars were computed in the same way as \ref{DailyAveragedDstEvents}.  In this plot, the overall trend is similar to that found in the bottom panel of \ref{HourlyAveragedDstEvents} - $\rho_{eq}$ is slighly elevated at the time of the threhshold crossing of $D_{st}$ with respect to the values one day before and after, but the elevation is small and in general not statistically significant.  At this timescale no obvious change in mass density at hourly timescale is visible. This points to an issue with only looking at long-timescale trends between density and $D_{st}$, and allows for the possibility that other factors are influencing the long term correlation because there is no obvious connection on a short timescale.  One possibility is that, as suggested in \cite{Takahashi2010}, $F_{10.7}$ plays a significant role in driving long term density values which biases the long-term correlation of density and $D_{st}$.

Results of test on different between means of $\rho_{eq}$ shown in the bottom panel of \ref{DailyAverage} on days near or on the day of a $D_{st}$ event.

@@

\begin{figure}[htp!]
\centering
\includegraphics[scale=0.45]{paperfigures/alldata-GOES6-1983-1991.eps}
\caption{Overview of data used in this study. The top four panels show parameters from \cite{Kondrashov2014ReconstructionOfGaps} and the bottom panel contains $\rho_{eq}$ based on GOES 6 measurements from \cite{Denton} after interpolation and averaging described in the text. Dashed horizontal lines in the $D_{st}$ and $\rho_{eq}$ panels indicate sample event cutoff thresholds of $D_{st} = -50$~nT and $\rho_{eq} = 20$~amu/cm$^3$}.
\label{AllData}
\end{figure}
